Negative Selection in the 20th Century

### 2020-05-19 why-negative-selection.Rmd
Improve GHS weights. Weight by age/sex/educ and by age at first live birth (women).

* Work more on weighting the data?
  - weight by age at first live birth
  - education using ISCED?
  - geography?
  - ask for existing work by others?

@@

@@

@@

Effect sizes tend to be smaller for children regressions. This
could be caused by ascertainment bias in the UK Biobank sample -- e.g.,
if respondents themselves are a more selected sample than the respondents' 
parents. To check this, we weighted UK Biobank participants by age of leaving
full time education. Our sample weights are based on the 2006 General Household
Survey, calculating proportions within age and sex cells among White British
respondents. We then rerun the basic *children* regressions.

Figure \@ref(fig:plot-weighted) shows the results, with unweighted estimates
plotted for comparison. Weighting increases effect sizes on average by 
`r 100 * (mean_prop_wtd_unwtd - 1)` per cent. These weights are only basic 
attempts to correct for ascertainment bias. Effect sizes might be increased 
further by more precise weighting.

@@

>>>>

* Work more on weighting the data
  - ask for existing work by others?
  - deal with the fact that GHS 06 has its own weights and use
    subset.svydesign to reweight?

@@

## Paper plan

* Intro: changes in PGS over time
* We investigate using n siblings and n children. Effect sizes are much larger
  for n siblings.
  - This isn't because of change over time. (Details in appendix.)
  - Instead we hypoth that it is due to selection bias.
* To support this argument, we show that the strength of selection 
  varies dramatically across social groups.
  - Women more than men.
  - Effect sizes are larger among less educated and poorer respondents. (Appendix.)
  - Effect sizes are reversed in people with less than median sexual partners.
  - Effect sizes are reversed if we control for age at first live birth.
  - There are strong effects of PGS on age at flb, both among respondents and
    their parents
* The UK Biobank sample is highly selected with respect to education, income
  and age at FLB. (Show using GHS.)
  - GHS variable for age at CHBNBM1; raw data babdata
* We reweight the data to get more accurate estimates.
* The data can be explained by a story where...
  -

@@

Effect sizes tend to be smaller for children regressions. This could be caused
by ascertainment bias in the UK Biobank sample -- e.g., if respondents
themselves are a more selected sample than the respondents' parents. To check
this, we weighted UK Biobank participants by sex, age (within the 40-71 age
group), and education. Our sample weights are calibrated based on the 2006
General Household Survey. We then rerun the basic *children* regressions.

@@

Figure \@ref(fig:plot-weighted) shows the results, with unweighted estimates
plotted for comparison. Weighting increases effect sizes on average by 
`r 100 * (mean_prop_wtd_unwtd - 1)` per cent.

@@

We also weighted data by age at first live birth and age, among women only.
These weights are only basic attempts to correct for ascertainment bias. Effect
sizes might be increased further by more precise weighting.

```{r plot-flb-weights, fig.cap = "Effect sizes on number of children, female respondents weighted by age at first live birth"}

drake::loadd(res_flb_weights)
drake::loadd(res_sex)

bind_rows(
        Weighted   = res_flb_weights, 
        Unweighted = res_sex %>% filter(sex == "Female") %>% select(-subset, - sex),
        .id        = "Regression"
      ) %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs(1))
      ) %>% 
      ggplot(aes(estimate, term, fill = Regression, 
        color = p.value < 0.05/66)) +
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs()
```
